Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

\begin{lemma} \label{lmm:hv:type1:cross-non-empty}
    Let $r_i$ be the full rectangle of $r_i'$ for each $i \in [k-2]$. All the following statements are true:
    \myenums{
        \item $\cross(\bm{t}, H) \ne \emptyset$ and $\cross(\bm{t}, V) \ne \emptyset$.
        \item For any $h \in \cross(\bm{t}, H)$ and $v \in \cross(\bm{t}, V)$, the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.
        \item If a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $h \in \cross(\bm{t}, H)$ and $v \in \cross(\bm{t}, V)$.
    }
\end{lemma}

@@

Equipped with the above, we can generate the target $S$ as follows:

\mytab{
    \> {\bf Algorithm Generate-$S$} \\
    \> 1.\> $S = \emptyset$ \\ 
    \> 2.\> {\bf for} each $(r_1, ..., r_{k-2}) \in \Pi_{1:k-2}(\J_1(R_1,$ $...,$ $R_{k-2}, H, V))$ {\bf do} \\
    \> 3.\>\> define $B, r_a$, and $r_b$ as above \\
    \> 4.\>\> {\bf for} each $(h, v) \in \cross(r_a, B; H) \times \cross(r_b, B; V)$ {\bf do} \\
    \> 5.\>\>\> add $(r_1, ..., r_{k-2}, h, v)$ to $S$
}

>>>>

\begin{lemma} \label{lmm:hv:type1:properties}
    Let $r_i$ be the full rectangle of $r_i'$ for each $i \in [k-2]$. All the following statements are true:
    \myenums{
        \item $\cross(\bm{t}, H) \ne \emptyset$ and $\cross(\bm{t}, V) \ne \emptyset$.
        \item For any $h \in \cross(\bm{t}, H)$ and any $v \in \cross(\bm{t}, V)$, the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.
        \item If a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $h \in \cross(\bm{t}, H)$ and $v \in \cross(\bm{t}, V)$.
    }
\end{lemma}

@@

Equipped Lemma~\ref{lmm:hv:type1:properties}, we can generate the target $S$ as follows:

\mytab{
    \> {\bf Algorithm Generate-$\J^*$} \\
    \> 1.\> $S = \emptyset$ \\ 
    \> 2.\> {\bf for} each $(r_1, ..., r_{k-2}) \in \Pi_{1:k-2}(\J_1(R_1,$ $...,$ $R_{k-2}, H, V))$ {\bf do} \\
    \> 3.\>\> define $B, r_a$, and $r_b$ as above \\
    \> 4.\>\> {\bf for} each $(h, v) \in \cross(r_a, B; H) \times \cross(r_b, B; V)$ {\bf do} \\
    \> 5.\>\>\> add $(r_1, ..., r_{k-2}, h, v)$ to $S$
}
